---
title: "Cool School"
author: "Shakespeare"
date: "November 20, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
    theme: "cosmo"
    # css: [file1.css, file2.css]
  pdf_document:
    toc: yes
params:
    client: "default"
---

```{r set-options}
knitr::opts_chunk$set(cache=TRUE)
```

```{css}
strong {
    color: red;
}
```

Markdown was made by Yihui Xie


# Show Parameters

```{r show-client,cache=FALSE}
sprintf("This report generated for %s.", params$client)
```

```{r render-with-parameters,eval=FALSE}
rmarkdown::render(input='MarkdownPrimer.Rmd', output_file='MarkdownSpecial.html', params=list(client='NYR'))
```


# Sections

Create a new section with a single hashtag. All words in a single line of code is a single paragraph.

Leave a blank line to start a new paragraph.

# Another Section {-}

Start a new section with another hashtag. No need to close the previous section.

# Subsections {.tabset}

We start subsections, which are nested within sections, with two hashtags.

## My First Subsection

Since this was started with two hashtags, it is a subsection beneath the prior section.

## Next Subsection

Just like with sections, start a subsection with two hashtags. No need to close the prior subsection.

# Back to Sections

Start a new section with a hashtag. Once again, don't worry about closing the preior subsection or section even.

# Lists {#list-info}

There are two primary types of lists: unordered and ordered.

## Unordered Lists

- Landlord
- Duvel
- Chimay
- St Sixtus
- Westmalle
- TEA

## Ordered

1. New York
    a. Coal
    a. Gas
    a. Wood
1. New Jersey
    - Gas
    - Wood
1. Philadelphia
1. Naples
    - Wood
1. Detroit
1. Roma

# Formatting

Text inside _single underscores_ appears as emphasized text

Two __underscores__ makes strong, which happens to look bold by default

Three ___underscores does both___

Backticks make the `text look like computer code` which is helpful

# Links

[My Webstie](https://www.jaredlander.com)

This link goes to our [section about lists](#list-info)

# Math

$$
\bar{x} = \frac{1}{n} \sum_{i=1}^n x_i
$$


$$
\begin{bmatrix}
1 & x_{11} & x_{12} & \dots & x_{1p} \\
1 & x_{21} & x_{22} & \dots & x_{2p}
\end{bmatrix}
$$

$$
y = f(x) = \alpha + \beta_1x_1 + \epsilon + \gamma + \Gamma + \pi + \Pi
$$

# R Time!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r simple-maths}
1 + 1
2*3
```

Let's play with variables

```{r variables,comment=NA}
x <- 3
x
```

Can we use `x` in subequent chunks?

```{r use-variables,cache=FALSE}
# this is a comment in a chunk
# because chunks are regular R code
x + 1
```

<!-- And this is a comment in markdown -->

What if we want to show the results of code, but not the code?

```{r hide-this,echo=FALSE,dependson=c('vairables')}
3*x + 8
```

# Plots Yes!

```{r diamond-scatter,fig.cap="Scatterplot of price vs size and cut",fig.scap="Scatterplot of diamonds",cache=TRUE}
library(ggplot2)
ggplot(diamonds, aes(x=carat, y=price, color=cut)) + 
    geom_point()
```

```{r working-dir}
getwd()
list.files()
here::here('data', 'TomatoFirst.csv')
```


```{r read-data,cache=TRUE, cache.extra=file.info(here::here('data', 'TomatoFirst.csv'))$mtime}
tomato <- readr::read_csv(here::here('data', 'TomatoFirst.csv'))
```


What an awesome plot
